Respiratory Disease Outbreaks in Toronto Pre, During, and Post Covid-19 Pandemic 

### 2025-05-13 paper/paper.qmd
added rough code for graphs

import numpy as np
import matplotlib.pyplot as plt

r = np.arange(0, 2, 0.01)
theta = 2 * np.pi * r
fig, ax = plt.subplots(
  subplot_kw = {'projection': 'polar'} 
)
ax.plot(theta, r)
ax.set_rticks([0.5, 1, 1.5, 2])
ax.grid(True)
plt.show()
```

@@

*insert table showing first few lines of raw data

@@

*** insert table

Below are the summary statistics for the cleaned data:

*** insert summary statistics

@@

Total & respiratory & Coronavirus:
*** insert graph

>>>>

@@

Below is an example of the raw data from 2019:

import polars as pl
import matplotlib.pyplot as plt

raw_data = pl.read_csv("Donalson-Paper/data/01-raw_data/ob_report_" + "2019" + ".csv")
raw_data = raw_data.head(5)
example_data = raw_data.to_dict(as_series = False)
plt.table(example_data)

plt.show()
```

@@

```{python}
#| label: disease-count-preview
#| fig-cap: "A line plot on a polar axis"

import polars as pl
import matplotlib.pyplot as plt

raw_data = pl.read_csv("Donalson-Paper/data/02-analysis_data/disease_count.csv")
raw_data = raw_data.head(5)
example_data = raw_data.to_dict(as_series = False)
plt.table(example_data)

plt.show()
```
```{python}
#| label: yearly-count-preview
#| fig-cap: "A line plot on a polar axis"

import polars as pl
import matplotlib.pyplot as plt

raw_data = pl.read_csv("Donalson-Paper/data/02-analysis_data/yearly_disease_count.csv")
raw_data = raw_data.head(5)
example_data = raw_data.to_dict(as_series = False)
plt.table(example_data)

plt.show()
```

Below are the summary statistics for the cleaned yearly count data:

```{python}
#| label: yearly-count-summary-statistics
#| fig-cap: "A line plot on a polar axis"

import polars as pl
import matplotlib.pyplot as plt

raw_data = pl.read_csv("Donalson-Paper/data/02-analysis_data/yearly_disease_count.csv")
summary_data = raw_data.describe()
summary_data = summary_data.to_dict(as_series = False)
plt.table(summary_data)

plt.show()
```

@@

Total & respiratory & Coronavirus:
```{python}
#| label: corona-resp-total-graph
#| fig-cap: "A line plot on a polar axis"

import polars as pl
import matplotlib.pyplot as plt
import np as np

t = np.arange(2019, 2025, 1)
KEYS = ["Coronavirus", "Respiratory", "Total"]
raw_data = pl.read_csv("Donalson-Paper/data/02-analysis_data/yearly_disease_count.csv")
for key in KEYS:
  plt.plot(t, raw_data[key], label = key, {'marker': 'o'})

plt.set_title("Coronavirus, Respiratory & Total Outbreaks")
plt.set_xlabel("Year")
plt.set_ylabel("Outbreak Count")
plt.grid()

plt.legend()
plt.show()
```
